Live Functional Programming with Typed Holes

### 2018-04-30 discussion.tex
better wording in acks

The authors would like to thank Brigitte Pientka, Jonathan Aldrich, Joshua Sunshine, Michael Hilton, Claire LeGoues, the participants of the PL reading group at UChicago, and referees and participants of the LIVE 2017 and Off the Beaten Track (OBT) 2017 workshops for their insights and feedback on various iterations of this work.

>>>>

The authors would like to thank Brigitte Pientka, Jonathan Aldrich, Joshua Sunshine, Michael Hilton, Claire LeGoues, the participants of the PL reading group at UChicago, and the referees and participants of the LIVE 2017 and Off the Beaten Track (OBT) 2017 workshops for their insights and feedback on various iterations of this work.
